Efficient pedigree recording for fast population genetics simulation

### 2018-01-04 forwards_paper.tex
Address some comments on the PR
added parens, closes #48

%% Progressive memory reduction as a function of T
To get an idea of how required space depends on the length of time between simplification steps,
suppose instead that we have run a simulation of $2N$ individuals for $T$ generations,
begun with no prior history.
How many of the resulting $4NT$ edges are required after simplification?
As above, the expected number of edges is bounded by $2N-2$ plus four times the mean marginal tree length.
Roughly, the length of time for which a marginal tree has $k$ tips is
$2N/k(k-1) = 2N(1/(k-1) - 1/k)$,
and so the time to go from $N$ to $n$ tips is $2N(1/(n-1) - 1/(N-1))$.
This implies that after running for time $T$ we expect to
have around $n(T)$ roots, where $n(T) \approx 1 + 2N/(T+2)$.
The total tree length over this time is
$2 N \sum_{k=n(T)+1}^{N-1} 1/k$, which
% is approximately
% \begin{align*}
%     2 N \log\left( \frac{N}{1 + 2 N/(T+2)} \right) .
% \end{align*}
leads to an upper bound on the number of edges of
\begin{align}
    \label{eqn:edge_bound}
    2 N \left( 1 + 4 \log\left( \frac{NT}{T + 2 N} \right)\right) .
\end{align}
These calculations hold up quite well in practice,
as shown in Figure~\ref{fig:simplify_complexity}.
% by comparison to
% the number of edges actually required for 50 independent Wright--Fisher simulations,
% as a function of time (obtained from Algorithm~\algref{W} with $s=1$)
% is shown in Figure~\ref{fig:simplify_complexity}, compared to this prediction.

@@

\section{Effect of simplification interval on run time and memory use}
\label{ss:gcinterval}

We performed a limited set of simulations to explore the effect of the simplification interval on run times and memory
use. Figure~\ref{sfig:gctime} shows that run times increase for simplification intervals less than 100 generations.  For
intervals $\geq 100$ generations, run times are very similar, with no appreciable difference between $10^3$ and $10^4$
generations.  As expected, the simplification interval has a near-linear effect on peak RAM use
(Figure~\ref{sfig:gcmem}).  Taken together Figures~\ref{sfig:gctime} and~\ref{sfig:gcmem} suggest that one can tune the
simplification interval to available RAM with little effect on run times provided that simplification doesn't occur too
often.

@@

\newpage
\section{Timing and memory use with no selection}
\label{ss:timing_nosel}
\renewcommand{\thefigure}{C\arabic{figure}}
\setcounter{figure}{0}

>>>>

%% Progressive memory reduction as a function of T
To get an idea of how required space depends on the length of time between simplification steps,
suppose instead that we have run a simulation of $2N$ individuals for $T$ generations,
begun with no prior history.
How many of the resulting $4NT$ edges are required after simplification?
As above, the expected number of edges is bounded by $2N-2$ plus four times the mean marginal tree length.
Roughly, the length of time for which a marginal tree has $k$ tips is
$2N/(k(k-1)) = 2N(1/(k-1) - 1/k)$,
and so the time to go from $N$ to $n$ tips is $2N(1/(n-1) - 1/(N-1))$.
This implies that after running for time $T$ we expect to
have around $n(T)$ roots, where $n(T) \approx 1 + 2N/(T+2)$.
The total tree length over this time is
$2 N \sum_{k=n(T)+1}^{N-1} 1/k$, which
% is approximately
% \begin{align*}
%     2 N \log\left( \frac{N}{1 + 2 N/(T+2)} \right) .
% \end{align*}
leads to an upper bound on the number of edges of
\begin{align}
    \label{eqn:edge_bound}
    2 N \left( 1 + 4 \log\left( \frac{NT}{T + 2 N} \right)\right) .
\end{align}
These calculations hold up quite well in practice,
as shown in Figure~\ref{fig:simplify_complexity}.
% by comparison to
% the number of edges actually required for 50 independent Wright--Fisher simulations,
% as a function of time (obtained from Algorithm~\algref{W} with $s=1$)
% is shown in Figure~\ref{fig:simplify_complexity}, compared to this prediction.

@@

\section{Effect of simplification interval on run time and memory use}
\label{ss:gcinterval}
\renewcommand{\thefigure}{C\arabic{figure}}

We performed a limited set of simulations with \fwdpy{} to explore the effect of the simplification interval on run times and memory
use. Figure~\ref{sfig:gctime} shows that run times increase for simplification intervals less than 100 generations.  For
intervals $\geq 100$ generations, run times are very similar, with no appreciable difference between $10^3$ and $10^4$
generations.  As expected, the simplification interval has a near-linear effect on peak RAM use
(Figure~\ref{sfig:gcmem}).  Taken together Figures~\ref{sfig:gctime} and~\ref{sfig:gcmem} suggest that one can tune the
simplification interval to available RAM with little effect on run times provided that simplification doesn't occur too
often.

@@

\newpage
\section{Timing and memory use with no selection}
\label{ss:timing_nosel}
\renewcommand{\thefigure}{D\arabic{figure}}
\setcounter{figure}{0}
